Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-22 paper/paper.tex
Summing up ommited results

>>>>

\section{Ommited results}

\begin{enumerate}
  \item The lower bound of $\Omega(\ell)$ for the scenario with at most $(1/3-1/k)$-augmentation
  \item Costly cascade example (it is easy to present $k^2$ and $k\cdot \sqrt{k}$ (with different approach), and then we can combine these to obtain $k^3$)
  \item $k$-competitive algorithm for the ring communication pattern
  \item $O(\ell)$-competitive algorithm for $k=4$ and $k=5$
\end{enumerate}
